---
title: "575 Final Project - Global Optimism for Nuclear Power"
author: "Joshua Inwald"
date: "Sys.Date()"
output: html_document
---

## Project Overview

In this project, I run analyses on a global dataset to understand how concern for nuclear power varies around the globe. What types of people are most afraid of nuclear power? Do either concern for climate change or trust in one's government to effectively manage public safety (novel predictors) predict optimism vs pessimism for nuclear power? How do these factors vary across countries?

```{r setup, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#Load package libraries
library(tidyverse)
library(psych)
library(lme4)
library(lmerTest)
library(simr)
library(psych)
library(GPArotation)
library(multilevel)
library(mediation)
library(MuMIn)
library(sjstats)
library(usethis)
library(wCorr)
library(modelsummary)
library(AICcmodavg)
library(Rgraphviz)
library(merTools)
library(phantomjs)
library(glmmTMB)
library(brms)
library(broom.mixed)
library(htmlwidgets)
library(lattice)
use_git_config(user.name="JoshuaInwald", user.email = "inwald@usc.edu")
setwd("~/Documents/Multilevel Modeling/575 Final Project")
```

```{r prep}
####################################################################################################
#Data prep and cleaning

#Read in data
mydata <- read.table("lrf_public_file_review.tab", header = TRUE, fill = TRUE, sep = "\t")

# Nuclear power concern DV trinary recode-ing
mydata <- mydata %>%
  mutate(NukeOptimism = if_else((L4B == 4 | L4B == 98 | L4B == 99),"0",  #Treats the "neither" + "don't know" + "don't have an opinion" folks as zeros, vs N/As
                                if_else((L4B == 3),"0",
                                        if_else((L4B == 2),"-1", "1"))))
mydata$NukeOptimism <- as.numeric(mydata$NukeOptimism)
# Nuclear power concern DV binary recode-ing
mydata <- mydata %>%
  mutate(NukeBinary = if_else(NukeOptimism == 1,1,0))
mydata$NukeBinary <- as.numeric(mydata$NukeBinary)

# Research question 1: Demographic controls (age and education; gender, income quintiles and World Bank country income brackets are already okay)
mydata$Age <- as.numeric(ifelse(mydata$Age>99,NA,mydata$Age))
mydata$Education <- as.numeric(ifelse(mydata$Education>3,NA,mydata$Education)) #Exclude I don't knows / did not responds

# Mutate variable to indicate countries with active civilian nuclear power plants in 2021
NukeCountries <- c("Argentina", "Armenia", "Belarus", "Belgium", "Brazil", "Bulgaria", "Canada", "China", "Finland", 
                   "France", "Germany", "Hungary", "India", "Iran", "Japan", "South Korea", "Mexico", "Netherlands", 
                   "Pakistan", "Romania", "Russia", "Slovakia", "Slovenia", "South Africa", "Spain", "Sweden", 
                   "Switzerland", "Taiwan", "Ukraine", "United Arab Emirates", "United Kingdom", "United States")
mydata <- mydata %>%
  mutate(NuclearCountry = if_else(mydata$Country %in% NukeCountries,1,0))
mydata$NuclearCountry <- as.numeric(mydata$NuclearCountry)

# Research question 2: Climate change recoding
mydata <- mutate(mydata, CCConcern = if_else((L5 == 3 | L5 == 98 | L5 == 99),0, 1)) #Climate Change, using a binary re-code
mydata$CCConcern <- as.numeric(mydata$CCConcern)

# Research question 3: Belief in government safety regulations efficacy
mydata$L16A <- if_else((mydata$L16A == 1), 1,0)
mydata$L16B <- if_else((mydata$L16B == 1), 1,0)
mydata$L16C <- if_else((mydata$L16C == 1), 1,0)
omega(m = mydata[c("L16A", "L16B", "L16C")]) #Beliefs in gov safety efficacy: alpha = 0.77, omega = 0.78 
mydata <- mydata %>%
  mutate(GovSafeEff = L16A + L16B + L16C)
```

## RQ1

```{r Q1models}
#RQ 1 MODELING
m0 <- lmer(NukeOptimism ~ Age + as.factor(Education) + as.factor(Gender) + (1 | Country), 
           data=mydata, REML = FALSE)
#summary(m0)$AIC = 368703.5
#ICC calculation
variance_components <- as.data.frame(VarCorr(m0))
between_var <- variance_components$vcov[1]
within_var <- variance_components$vcov[2]
icc <- between_var / (between_var + within_var)
#ICC = 0.09 || ICC = 0.06981 / (0.06981+0.65151)

m1 <- lmer(NukeOptimism ~ Age + as.factor(Education) + as.factor(Gender) + 
             as.factor(INCOME_5) + (1 | Country), 
           data=mydata, REML = FALSE)
#summary(m1)$AIC = 366017.4

m2 <- lmer(NukeOptimism ~ Age + as.factor(Education) + as.factor(Gender) + 
             as.factor(CountryIncomeLevel) + (1 | Country), 
           data=mydata, REML = FALSE)
#summary(m2)$AIC = 368678.7

m3 <- lmer(NukeOptimism ~ Age + as.factor(Education) + as.factor(Gender) + 
             as.factor(NuclearCountry) + (1 | Country), 
           data=mydata, REML = FALSE)
#summary(m3)$AIC = 368703.8

m4 <- lmer(NukeOptimism ~ Age + as.factor(Education) + as.factor(Gender) + 
             as.factor(CountryIncomeLevel) + as.factor(INCOME_5) + as.factor(NuclearCountry) + (1 | Country), 
           data=mydata, REML = FALSE)
#summary(m4)$AIC = 365983.1

#AIC comparison using AICcmodavg package: recommendation = fullest model, despite income quintiles not yielding significant betas
models <- list(m0,m1,m2,m3,m4)
model.names <- c("basic","+income","+WorldBank","+CivilNuke","+everything")
AICcmodavg::aictab(cand.set = models, modnames = model.names)

#Full model R-squared = 0.11
performance::r2(m4)

#msummary table for base model
msummary(m4, estimate = "{estimate}{stars}",
         statistic = NULL, title = "Controls-only Model", 
         coef_rename = c("as.factor(Gender)2"="Female gender (vs male)",
                         "as.factor(Education)2"="High school education (vs primary school)",
                         "as.factor(Education)3"="College education (vs primary school)",
                         "as.factor(CountryIncomeLevel)2"="Lower-middle income country (vs lower-income)",
                         "as.factor(CountryIncomeLevel)3"="Upper-middle income country (vs lower-income)",
                         "as.factor(CountryIncomeLevel)4"="Upper income country (vs lower-income)",
                         "as.factor(INCOME_5)2" = "2nd income quintile (vs 1st)",
                         "as.factor(INCOME_5)3" = "3rd income quintile (vs 1st)",
                         "as.factor(INCOME_5)4" = "4th income quintile (vs 1st)",
                         "as.factor(INCOME_5)5" = "5th income quintile (vs 1st)",
                         "as.factor(NuclearCountry)1" = "Civilian Nuclear Power (vs not)"))
```

## Base Model Equation

$$ NuclearOptimism_{ij} = \beta_{0j} + \beta_{1j} * Age_{ij} + \beta_{2j} *Education_{ij} + \\ \qquad \qquad \qquad \qquad \quad \beta_{3j} *Gender_{ij} + \beta_{4j} *Income_{ij} + e_{ij} \\
\beta_{0j} = \gamma_{00} + \gamma_{01}*WorldBank_{j} + \gamma_{02}*CivilianNuclear_{j} + u_{0j} \\
\beta_{1j} = \gamma_{10} \\
\beta_{2j} = \gamma_{20} \\
\beta_{3j} = \gamma_{30} \\
\beta_{4j} = \gamma_{40}
$$

## RQ2

```{r RQ2}
#RQ 2 Climate Change

# Decompose climate change concern into country-means + country-mean-centered
mydata <- mydata %>% 
  group_by(Country) %>% 
  mutate(CCConcern_cm = mean(CCConcern),   # create cluster means
         CCConcern_cmc = CCConcern - CCConcern_cm) %>%   # cluster-mean-centered
  ungroup()

#Model nuclear optimism with climate change concern as a random slope, decomposed into country-means and country-mean-cenetered values
m5 <- lmer(NukeOptimism ~ Age + as.factor(Education) + as.factor(Gender) + 
             CCConcern_cm + CCConcern_cmc + (CCConcern_cmc | Country) +
             as.factor(CountryIncomeLevel) + as.factor(INCOME_5) + as.factor(NuclearCountry), 
           data=mydata, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
#summary(m5)

#LRT on climate change concern random slopes
# model WITH random slopes = m5, deviance = summary(m5)$AIC[4]
m5.5 <- lmer(NukeOptimism ~ Age + as.factor(Education) + as.factor(Gender) + 
               CCConcern_cm + CCConcern_cmc + (1 | Country) +
               as.factor(CountryIncomeLevel) + as.factor(INCOME_5) + as.factor(NuclearCountry), 
             data=mydata, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
# model WITHOUT random slopes = m5.5, deviance = summary(m5.5)$AIC[4]

#LRT = deviance emptier - deviance fuller
pchisq(unname(summary(m5.5)$AIC[4])-unname(summary(m5)$AIC[4]), df = 2, lower.tail=FALSE) / 2 #df = 2 because of tau0 &, tau1-squared parameters
#mega-significant! LRT supports inclusion of random slopes

#CC model R-squared = 0.11
performance::r2(m5)

#Table of coefficients for main models so far
msummary(list("Base Model" = m4,"Base + Climate Change Concern" = m5), 
         estimate = "{estimate}{stars}",
         statistic = NULL, title = "Controls-only vs Climate Change Concern", 
         coef_rename = c("as.factor(Gender)2"="Female gender (vs male)",
                         "as.factor(Education)2"="High school education (vs primary school)",
                         "as.factor(Education)3"="College education (vs primary school)",
                         "as.factor(CountryIncomeLevel)2"="Lower-middle income country (vs lower-income)",
                         "as.factor(CountryIncomeLevel)3"="Upper-middle income country (vs lower-income)",
                         "as.factor(CountryIncomeLevel)4"="Upper income country (vs lower-income)",
                         "as.factor(INCOME_5)2" = "2nd income quintile (vs 1st)",
                         "as.factor(INCOME_5)3" = "3rd income quintile (vs 1st)",
                         "as.factor(INCOME_5)4" = "4th income quintile (vs 1st)",
                         "as.factor(INCOME_5)5" = "5th income quintile (vs 1st)",
                         "as.factor(NuclearCountry)1" = "Civilian Nuclear Power (vs not)"))
```

##RQ3

```{r RQ3}
#RQ 3 Trust in government safety efficacy
describe(mydata$GovSafeEff)

# Decompose trust-in-government into country-means + country-mean-centered
mydata <- mydata %>% 
  group_by(Country) %>% 
  mutate(GovSafeEff_cm = mean(GovSafeEff),   # create cluster means
         GovSafeEff_cmc = GovSafeEff - GovSafeEff_cm) %>%   # cluster-mean-centered
  ungroup()

#Model nuclear optimism with trust-in-government as a random slope, decomposed into country-means and country-mean-cenetered values
m6 <- lmer(NukeOptimism ~ Age + as.factor(Education) + as.factor(Gender) + 
             GovSafeEff_cm + GovSafeEff_cmc + (GovSafeEff_cmc | Country) +
             as.factor(CountryIncomeLevel) + as.factor(INCOME_5) + as.factor(NuclearCountry), 
           data=mydata, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
#summary(m6)

#LRT on trust-in-government random slopes
# model WITH random slopes = m6, deviance = summary(m6)$AIC[4]
m6.5 <- lmer(NukeOptimism ~ Age + as.factor(Education) + as.factor(Gender) + 
               GovSafeEff_cm + GovSafeEff_cmc + (1 | Country) +
               as.factor(CountryIncomeLevel) + as.factor(INCOME_5) + as.factor(NuclearCountry), 
             data=mydata, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
# model WITHOUT random slopes = m6.5, deviance = summary(m6.5)$AIC[4]

#LRT = deviance emptier - deviance fuller
pchisq(unname(summary(m6.5)$AIC[4])-unname(summary(m6)$AIC[4]), df = 2, lower.tail=FALSE) / 2 #df = 2 because of tau0 &, tau1-squared parameters
#mega-significant! LRT supports inclusion of random slopes

#CC model R-squared = 0.12 -- movin' up in the world
performance::r2(m6)

#Cross-level interaction between trust-in-government (L1) and whether a country has civilian nuclear power (L2)
m7 <- lmer(NukeOptimism ~ Age + as.factor(Education) + as.factor(Gender) + 
             GovSafeEff_cm + GovSafeEff_cmc*as.factor(NuclearCountry) + (GovSafeEff_cmc | Country) +
             as.factor(CountryIncomeLevel) + as.factor(INCOME_5) + as.factor(NuclearCountry), 
           data=mydata, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
summary(m7)
#Zero significance, which is a shame, and also surprising? 
#I expected nuclear-capable countries to differ from non-nuclear countries in terms of how their citizens view government safety
```

##RQ4

```{r RQ4}
####################################################################################################
#RQ 4 Compare models 

#Base model AIC: summary(m4)$AIC = 365983.1 | performance::r2(m4) R2 = 0.11 | n = 151663
#Climate change random slopes AIC: summary(m5)$AIC = 364666.5 | performance::r2(m5) R2 = 0.11 | n = 151663
#Trust-in-government random slopes AIC: summary(m6)$AIC = 359945.5 | performance::r2(m6) R2 = 0.12 | n = 149576

#Combo climate change concern + trust-in-government model
m8 <- lmer(NukeOptimism ~  CCConcern_cm + CCConcern_cmc + GovSafeEff_cm + GovSafeEff_cmc + 
             (CCConcern_cmc + GovSafeEff_cmc | Country) +
             Age + as.factor(Education) + as.factor(Gender) + as.factor(CountryIncomeLevel) + 
             as.factor(NuclearCountry) + as.factor(INCOME_5), 
           data=mydata, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
#summary(m8)$AIC = 358725.0 | performance::r2(m8) R2 = 0.12 | n = 149576

#Kitchen-sink data prep + model
mydata$Urbanicity <- if_else((mydata$Urbanicity == 9), NA,mydata$Urbanicity)
mydata <- mydata %>% 
  mutate(OverallSafetyFeeling = factor(L2, levels = c(1,2,3,98,99), 
                                       labels = c("More Safe", "Less Safe", "About as Safe", "About as Safe", "About as Safe")))
mydata <- mydata %>% #GMOs
  mutate(GMOOptimism = if_else((L4A == 4 | L4A == 98 | L4A == 99),"0",
                               if_else((L4A == 3),"0",
                                       if_else((L4A == 2),"-1", "1"))))
mydata$GMOOptimism <- as.numeric(mydata$GMOOptimism)
mydata <- mydata %>% #AI
  mutate(AIOptimism = if_else((L4C == 4 | L4C == 98 | L4C == 99),"0",
                              if_else((L4C == 3),"0",
                                      if_else((L4C == 2),"-1", "1"))))
mydata$AIOptimism <- as.numeric(mydata$AIOptimism)
mydata$Numeracy <- if_else((mydata$L12 == 3), 1,0)
mydata$GovSafeResp <- if_else((mydata$L15 == 1), 1,0)
mydata$SMuse <- if_else((mydata$L26 == 1), 1,0)

#Kitchen-sink model
m9 <- lmer(NukeOptimism ~  Urbanicity + as.factor(OverallSafetyFeeling) + GMOOptimism +
             AIOptimism + Numeracy + GovSafeResp + SMuse + Age +
             as.factor(Education) + as.factor(Gender) + as.factor(CountryIncomeLevel) + 
             as.factor(NuclearCountry) + as.factor(INCOME_5) + (1|Country), 
           data=mydata, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
#summary(m9)$AIC = 344541.1 | performance::r2(m9) R2 = 0.18 | n = 148547

#Combo + best findings from kitchen-sink approach -- FINAL MODEL
mFinal <- lmer(NukeOptimism ~  CCConcern_cm + CCConcern_cmc + GovSafeEff_cm + GovSafeEff_cmc + 
                 (CCConcern_cmc + GovSafeEff_cmc | Country) + GMOOptimism + 
                 AIOptimism + as.factor(NuclearCountry) + as.factor(Education) + as.factor(Gender) + 
                 as.factor(CountryIncomeLevel) + Age + as.factor(INCOME_5), 
               data=mydata, REML = FALSE, control = lmerControl(optimizer = "bobyqa"))
#summary(mFinal)$AIC = 346069.2 | performance::r2(mFinal) R2 = 0.18 | n = 149576
#NOTE: msummary breaks for models with multiple random slopes, thus I build a final-model output table by hand
merTools::RMSE.merMod(mFinal) #RMSE = 0.77

#AIC comparison using AICcmodavg package: recommendation = kitchen-sink model, but I think it's important to keep the novel predictors
models <- list(m4,m5,m6,m9,mFinal)
model.names <- c("base","+CCconcern","+TrustInGov","+KitchenSink","Final")
AICcmodavg::aictab(cand.set = models, modnames = model.names)

#Re-run final model with binary paramterization of DV / logit link function
#Start with glmmTMB
mFB_glmmTMB <- glmmTMB(NukeBinary ~  CCConcern_cm + CCConcern_cmc + GovSafeEff_cm + GovSafeEff_cmc + 
                     (CCConcern_cmc + GovSafeEff_cmc | Country) + GMOOptimism + 
                     AIOptimism + as.factor(NuclearCountry) + as.factor(Education) + as.factor(Gender) + 
                     as.factor(CountryIncomeLevel) + Age + as.factor(INCOME_5), 
                   data=mydata, family = binomial("logit"))
summary(mFB_glmmTMB)
#summary(mFB_glmmTMB)$AIC = 170084.91 | performance::r2(mFB_glmmTMB) R2 = 0.22 | n = 149576

msummary(mFB_glmmTMB, output = "glmmTMBFinal.jpg",
         estimate = "{estimate}{stars}",
         statistic = NULL, title = "Binary Reparamaterization of Final Model", 
         coef_rename = c("as.factor(Gender)2"="Female gender (vs male)",
                         "as.factor(Education)2"="High school education (vs primary school)",
                         "as.factor(Education)3"="College education (vs primary school)",
                         "as.factor(CountryIncomeLevel)2"="Lower-middle income country (vs lower-income)",
                         "as.factor(CountryIncomeLevel)3"="Upper-middle income country (vs lower-income)",
                         "as.factor(CountryIncomeLevel)4"="Upper income country (vs lower-income)",
                         "as.factor(INCOME_5)2" = "2nd income quintile (vs 1st)",
                         "as.factor(INCOME_5)3" = "3rd income quintile (vs 1st)",
                         "as.factor(INCOME_5)4" = "4th income quintile (vs 1st)",
                         "as.factor(INCOME_5)5" = "5th income quintile (vs 1st)",
                         "as.factor(NuclearCountry)1" = "Civilian Nuclear Power (vs not)"))

#Cross-check with glmer
mFB_glmer <- glmer(NukeBinary ~  CCConcern_cm + CCConcern_cmc + GovSafeEff_cm + GovSafeEff_cmc + 
                        (CCConcern_cmc + GovSafeEff_cmc | Country) + GMOOptimism + 
                        AIOptimism + as.factor(NuclearCountry) + as.factor(Education) + as.factor(Gender) + 
                        as.factor(CountryIncomeLevel) + Age + as.factor(INCOME_5), 
                      data=mydata, family = binomial, control = glmerControl(optimizer = "bobyqa"))
#summary(mFB_glmer)
msummary(mFB_glmer, output = "glmerFinal.jpg",
         estimate = "{estimate}{stars}",
         statistic = NULL, title = "Binary Reparamaterization of Final Model", 
         coef_rename = c("as.factor(Gender)2"="Female gender (vs male)",
                         "as.factor(Education)2"="High school education (vs primary school)",
                         "as.factor(Education)3"="College education (vs primary school)",
                         "as.factor(CountryIncomeLevel)2"="Lower-middle income country (vs lower-income)",
                         "as.factor(CountryIncomeLevel)3"="Upper-middle income country (vs lower-income)",
                         "as.factor(CountryIncomeLevel)4"="Upper income country (vs lower-income)",
                         "as.factor(INCOME_5)2" = "2nd income quintile (vs 1st)",
                         "as.factor(INCOME_5)3" = "3rd income quintile (vs 1st)",
                         "as.factor(INCOME_5)4" = "4th income quintile (vs 1st)",
                         "as.factor(INCOME_5)5" = "5th income quintile (vs 1st)",
                         "as.factor(NuclearCountry)1" = "Civilian Nuclear Power (vs not)"))

#Exactly the same outputs from glmmTMB and glmer -- good sign!

#Attempted to re-run the model using brms package, but R couldn't handle it (canceled code after 60 minutes of run time)
#mFB_TMB <- brm(NukeBinary ~  CCConcern_cm + CCConcern_cmc + GovSafeEff_cm + GovSafeEff_cmc + 
#                     (CCConcern_cmc + GovSafeEff_cmc | Country) + GMOOptimism + 
#                     AIOptimism + as.factor(NuclearCountry) + as.factor(Education) + as.factor(Gender) + 
#                     as.factor(CountryIncomeLevel) + Age + as.factor(INCOME_5), 
#                   data=mydata, family = bernoulli("logit"), seed = 42)
```

## Final Model Equation

$$ NuclearOptimism_{ij} = \beta_{0j} + \beta_{1j} * ClimateConcernCMC_{ij} + \beta_{2j} *TrustGovCMC_{ij} + \\ 
\beta_{3j} *AIOptimism_{ij} + \beta_{4j} *GMOOptimism_{ij} + \\ 
\beta_{5j} * Education_{ij} + \beta_{6j} * Age_{ij} + \beta_{7j} * Gender_{ij} + \beta_{8j} * PersonalIncome_{ij} + e_{ij} \\
\beta_{0j} = \gamma_{00} + \gamma_{01}*ClimateConcernCM_{j} + \gamma_{02}*TrustGovCM_{j} + \\
\gamma_{03}*WorldBank_{j}+ \gamma_{04}*CivilianNuclearPower_{j} + u_{0j} \\
\beta_{1j} = \gamma_{10} + u_{1j}\\ 
\beta_{2j} = \gamma_{20} + u_{2j}\\ 
\beta_{3j} = \gamma_{30} \quad \beta_{4j} = \gamma_{40} \quad \beta_{5j} = \gamma_{50} \\
\beta_{6j} = \gamma_{60} \quad \beta_{7j} = \gamma_{70} \quad \beta_{8j} = \gamma_{80}  \\
Var(u_{0j}) = \tau^2_{0}  \quad Var(u_{1j}) = \tau^2_{1}  \quad Var(u_{2j}) = \tau^2_{2}     \\
\begin{pmatrix} u_{0j} \\ u_{1j} \\ u_{2j} \end{pmatrix} 
\sim N \begin{pmatrix} \begin{bmatrix} 0 \\ 0 \\ 0 \end{bmatrix}, 
                    \begin{bmatrix} \tau^2_{0} & \tau_{01} & \tau_{02} \\ 
                    \tau_{01} & \tau^2_{1} & \tau_{12} \\
                    \tau_{02} & \tau_{12} & \tau^2_{2}
                    \end{bmatrix} \end{pmatrix} \\ 
e_i \sim N(0, \sigma)
$$


##Graphics

```{r graphics}
#GRAPHICS
GlobalNukeBinary <- mydata %>%
  group_by(Country) %>%
  summarise(mean = weighted.mean(NukeBinary, WGT), n = n())

GlobalNukeTrinary <- mydata %>%
  group_by(Country) %>%
  summarise(mean = weighted.mean(NukeOptimism,WGT), n = n())

#View(GlobalNukeBinary)
#Global mean using weighted average = 40% of people globally who are optimistic for nuclear power
summarise(mydata,weighted.mean(NukeBinary,projection_weight),n = n())

#reference final model
#lmer(NukeOptimism ~  CCConcern_cm + CCConcern_cmc + GovSafeEff_cm + GovSafeEff_cmc + 
#                 (CCConcern_cmc + GovSafeEff_cmc | Country) + GMOOptimism + 
#                 AIOptimism + as.factor(NuclearCountry) + as.factor(Education) + as.factor(Gender) + 
#                 as.factor(CountryIncomeLevel) + Age + as.factor(INCOME_5))

#Marginal model plots to check linearity assumption of climate change and trust-in-government variables
augment(mFinal) %>%
  ggplot(aes(x = CCConcern_cmc, y = NukeOptimism)) +
  geom_point(size = 0.7, alpha = 0.3) +
  geom_smooth(col = "blue", se = FALSE) + # blue line from data
  geom_smooth(aes(y = .fitted),
              col = "red",
              se = FALSE, linetype = "dashed")
augment(mFinal) %>%
  ggplot(aes(x = GovSafeEff_cmc, y = NukeOptimism)) +
  geom_point(size = 0.7, alpha = 0.3) +
  geom_smooth(col = "blue", se = FALSE) + # blue line from data
  geom_smooth(aes(y = .fitted),
              col = "red",
              se = FALSE, linetype = "dashed")

#Cluster residual plots to test equal variance of errors across clusters
Country1 <- c("Afghanistan","Albania","Algeria","Argentina","Armenia","Australia","Austria","Azerbaijan","Bahrain","Bangladesh","Belarus",
              "Belgium","Benin","Bolivia","Bosnia Herzegovina","Botswana","Brazil","Bulgaria","Burkina Faso","Cambodia","Cameroon",
              "Canada","Chad","Chile","China","Colombia","Congo Brazzaville","Costa Rica","Croatia","Cyprus","Denmark","Dominican Republic",
              "Ecuador","Egypt","El Salvador","Estonia")
Country2 <- c("Eswatini",	"Ethiopia",	"Finland",	"France",	"Gabon",	"Gambia"	,"Georgia",
              "Germany"	,"Ghana"	,"Greece"	,"Guatemala"	,"Guinea"	,"Honduras"	,"Hong Kong",
              "Hungary",	"India",	"Indonesia"	,"Iran"	,"Iraq"	,"Ireland",	"Israel"	,
              "Italy"	,"Ivory Coast",	"Jamaica",	"Japan"	,"Jordan"	,"Kazakhstan"	,
              "Kenya"	,"Kosovo"	,"Kuwait"	,"Kyrgyzstan"	,"Laos"	,"Latvia"	,"Lebanon",
              "Lesotho"	,"Liberia")
Country3 <- c("Libya",	"Lithuania"	,"Luxembourg"	,"Madagascar"	,"Malawi",	"Malaysia",
              "Mali",	"Malta"	,"Mauritania"	,"Mauritius",	"Mexico",	"Moldova"	,"Mongolia"	,
              "Montenegro",	"Morocco"	,"Mozambique"	,"Myanmar"	,"Namibia"	,"Nepal",
              "Netherlands",	"New Zealand",	"Nicaragua"	,"Niger",	"Nigeria",
              "North Macedonia"	,"Norway",	"Pakistan",	"Palestine"	,"Panama",
              "Paraguay",	"Peru",	"Philippines",	"Poland",	"Portugal"	,"Romania",
              "Russia",	"Rwanda")
Country4 <- c("Saudi Arabia",	"Senegal"	,"Serbia",	"Sierra Leone"	,"Singapore",
              "Slovakia",	"Slovenia",	"South Africa",	"South Korea",	"Spain"	,
              "Sri Lanka",	"Sweden",	"Switzerland"	,"Taiwan"	,"Tajikistan"	,"Tanzania",
              "Thailand",	"Togo",	"Tunisia",	"Turkey",	"Turkmenistan",	"Uganda",
              "Ukraine",	"United Arab Emirates",	"United Kingdom",	"United States",
              "Uruguay",	"Uzbekistan",	"Venezuela",	"Vietnam"	,"Yemen",	"Zambia",	"Zimbabwe")
augment(mFinal) %>%
  filter(Country %in% Country1) %>%
  ggplot(aes(x = factor(Country), y = .resid), 
         position=position_dodge(1)) +
  geom_boxplot() +
  coord_flip() 
augment(mFinal) %>%
  filter(Country %in% Country2) %>%
  ggplot(aes(x = factor(Country), y = .resid), 
         position=position_dodge(1)) +
  geom_boxplot() +
  coord_flip() 
augment(mFinal) %>%
  filter(Country %in% Country3) %>%
  ggplot(aes(x = factor(Country), y = .resid), 
         position=position_dodge(1)) +
  geom_boxplot() +
  coord_flip() 
augment(mFinal) %>%
  filter(Country %in% Country4) %>%
  ggplot(aes(x = factor(Country), y = .resid), 
         position=position_dodge(1)) +
  geom_boxplot() +
  coord_flip() 

#Normality of residuals
qqmath(mFinal)

#Illustrate variability in nuclear optimism across main predictor IVs
augment(m5, data = mydata) %>%
  ggplot(aes(x = CCConcern, y = NukeOptimism, color = factor(Country))) +
  geom_point(size = 0.2, alpha = 0.2) +
  geom_smooth(aes(y = .fitted),
              method = "lm", se = FALSE, size = 0.5) +
  stat_summary(aes(x = CCConcern_cm, y = .fitted,
                   fill = factor(Country)),
               color = "red", 
               fun = mean, 
               geom = "point",
               shape = 24,
               size = 2.5) +
  geom_smooth(aes(x = CCConcern_cm, y = .fitted),
              method = "lm", se = FALSE,
              color = "black") +
  labs(y = "Nuclear Optimism") +
  guides(color = "none", fill = "none")

augment(m6, data = mydata) %>%
  ggplot(aes(x = GovSafeEff, y = NukeOptimism, color = factor(Country))) +
  geom_point(size = 0.2, alpha = 0.2) +
  geom_smooth(aes(y = .fitted),
              method = "lm", se = FALSE, size = 0.5) +
  stat_summary(aes(x = GovSafeEff_cm, y = .fitted,
                   fill = factor(Country)),
               color = "red", 
               fun = mean, 
               geom = "point",
               shape = 24,
               size = 2.5) +
  geom_smooth(aes(x = GovSafeEff_cm, y = .fitted),
              method = "lm", se = FALSE,
              color = "black") +
  labs(y = "Nuclear Optimism", x = "Trust in Government") +
  guides(color = "none", fill = "none")


#Unused 
#mFinal %>%
#  augment(data = mydata) %>%
#  ggplot(aes(
#    x = GovSafeEff, y = .fitted, group = factor(Country),
#    color = factor(CountryIncomeLevel)  # use `sector` for coloring lines)) +
#  geom_smooth(method = "lm", se = FALSE, size = 0.5) +
#  labs(y = "Predicted Nuclear Optimism", color = "NuclearCountry")
```